### 2010-02-24 ChrisnaSections.tex
Finished covariates; onto best practices!

    %% COVARIATES:
    \subsection{Covariates}
    To determine the relative importance of our covariates (the observer, the
    date, and the number of days since the most recent snow event), we ran the
    standard hierarchical model with \(E\) on simulated data with values of
    \(\psi\) and \(\theta\) similar to our estimates of \(\psi\) and \(\theta\)
    on 2003's data with varying numbers of observers, snow events, and
    observations after each snow event.

    \subsection{Best Practices for Measuring Otter Occupancy}

>>>>

    %% COVARIATES:
    \subsection{Covariates}
    To determine the relative importance of our covariates (observer,
    date, and number of days since the most recent snow event), we ran the
    standard hierarchical model with \(E\) on simulated data with values of
    \(\psi\) and \(\theta\) similar to our estimates of \(\psi\) and \(\theta\)
    on 2003's data with varying numbers of observers, snow events, and
    observations after each snow event.  We assume that observations after each
    snow event will occur on consecutive days, starting from the first day after
    the snow event.  This information helped us to find the most efficient ways
    (with respect to number of flights) to gather aerial occupancy data given
    one, two, and three observers while still obtaining useful estimates from
    the model.

    The number of observers proved to be the least important of the three
    covariates.  We were able to obtain accurate estimates regardless of the
    number of observers, as long as there were sufficient numbers of snow events
    and observations after each snow event.  For one observer, at least three
    snow events and three observations on consecutive days after each snow event
    are required for the model to converge and give good estimates.  For two or
    three observers, two events with three observations on consecutive days
    after each snow event is sufficient.  Therefore, roughly nine, twelve, and
    eighteen flights are required to obtain good estimates for one, two, and
    three observers, respectively.  Surprisingly, the most cost-effective method
    (as measured by the number of flights required) only requires one observer.

    The number of snow events proved to be the second-most important of the
    three covariates.  Although two snow events are required, only with one
    observer does the addition of a third snow event noticeably affect the
    model's estimates.

    The number of observations after each snow event proved to be the most
    important of the three covariates.  Because the model relies upon the
    assumption that the probability of seeing a track increases each day because
    tracks made on previous days within the same snow event can still be seen,
    this is not surprising.  Two observations after each snow event on
    consecutive days are required.  Additional observations after each event
    help the model converge more quickly, but the estimates become only slightly
    more accurate.

    Additional observations are more helpful than additional snow events at
    first, although both are much more helpful than the addition of an observer.
    Once the numbers of snow events and observations after each snow event both
    surpass three, they improve the model's estimates at roughly equal rates.
    Note, however, that increasing the number of snow events is likely to be far
    less challenging than increasing the number of observations after each snow
    event at that point.

    \subsection{Best Practices for Measuring Otter Populations}
